A comparison of model-based and design-based approaches for spatial data.

### 2021-06-07 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
outline for introduction.
added some lit overview

@@

>>>>

define sampling design, define parameters, define model-based, etc.

introduction of spatial data / definition of spatial and maybe general background?

2-3 sentences about each design

goals and outline of paper

@@

* hansen1983evaluation - general overview (in non spatial context), talk about population vs superpopulation give a set of guiding principles in the discussion

* brus1997random - design and model based explanation and simulation study for spatial means, make a decision tree for choosing among approaches

* verhoef2002sampling - strictly defines classical sampling, compares FPBK to classical, BK to classical
